Investigating Neolithic pottery use from Guijiabao in the Yanyuan Basin in southwestern China using organic residue analysis

### 2023-04-16 analysis/paper/paper.Rmd
adjust the background color of figures

ggsave(plot = chroma_four,
       here::here("analysis","figures", "chromatograms_four.png"),
       width = 6,
       height = 8,
       dpi = 300,
       units = "in")
```

@@

ggsave(plot = chroma_specific,
       here::here("analysis","figures", "chromatograms_specific.png"),
       width = 8,
       height = 5,
       dpi = 300,
       units = "in")
```

@@

ggsave(here::here("analysis","figures","isotopic_plots.png"),
       width = 6,
       height = 8,
       dpi = 300,
       units = "in")
```

>>>>

ggsave(plot = chroma_four,
       here::here("analysis","figures", "chromatograms_four.png"),
       bg = "white",
       width = 6,
       height = 8,
       dpi = 300,
       units = "in")
```

@@

ggsave(plot = chroma_specific,
       here::here("analysis","figures", "chromatograms_specific.png"),
       bg = "white",
       width = 8,
       height = 5,
       dpi = 300,
       units = "in")
```

@@

ggsave(here::here("analysis","figures","isotopic_plots.png"),
       bg = "white",
       width = 6,
       height = 8,
       dpi = 300,
       units = "in")
```
